Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-18 doc/GMP2015/s05_problems.tex
Further proof reading. Fixed \emph problem!
Added the open questions to the conclusion

In the recombination setting, the corresponding \dfn{restricted
OMD$_k$  problem} requires the reduced graph $G'$ and its isostatic
completion $H$ to be 2-trees as in Section \ref{sec:2-tree-reduction}
or to be a low Cayley complexity tree-decomposable graph as in Section
\ref{sec:tdecomp}. Clearly these problems have deterministic
polynomial time algorithms, the algorithms run in time exponential in
$k$. As a result, when $k$ is part of the input, the \dfn{restricted
OMD problem} has the potential to be difficult. For example, when the
isostatic completion $H$ is required to be a 2-tree the restricted OMD
problem is reducible to the maximum spanning series-parallel subgraph
problem shown by \uncited\uncited to be NP-complete even if the input
graph is planar of maximum degree at most 6. However, since the OMD
problem has other input restrictions such as not having any proper
isostatic subgraphs, it is not clear if the reverse reduction exists
and hence it is unclear whether the OMD problem is NP-complete. The
same holds for the restricted OMD problem where the isostatic
completion $H$ is required to be a tree-decomposable graph of low
Cayley complexity (i.e, have special, small DR-plans). One potential
obstacle to an indecomposable graph $G$'s membership in the restricted
OMD$_k$ for small $k$ is if $G$ is tri-connected and has large girth.
In fact, 6-connected (hence rigid) graphs with arbitrarily large girth
have been constructed in \uncited.
%
\subsection{Optimal Modification, Completion and Recombination: formal
connections}
%
The OMD problem is closely related to a well-studied problem of
completion of an under-constrained system to an isostatic one with a
small DR-plan.
\begin{observation}
    The (decision version of) the {\bf optimal completion problem
    (OC)} from \cite{bib:survey, j-a, fang} is OMD$_0$.
\end{observation}.
In fact, a \dfn{restricted OC} problem was studied by \cite{j-a}
requiring the completion to be tree-decomposable. It is not clear if
the reverse reduction holds, i.e, is OMD reducible to OC?

@@

This reduction is used also for transferring  algorithms for optimal
DR-planning, recombination, completion, OMD, and other problems and to
so-called \dfn{multi-body pin} from so-called \dfn{bar-joint-systems},
by showing that the corresponding problems for the latter are reduced
to the corresponding problems on bar-joint systems.

\note This section deals only with bar-joint systems, however,
extensions of several of these problems, approaches and solutions to
other qusecs beyond  bar-joint - specifically pinned line incidence
systems and multi-body-pin systems will be expanded in Sections
\ref{sec:pinnedline} and \ref{sec:bodypin}.

>>>>

In the recombination setting, the corresponding \dfn{restricted
OMD$_k$  problem} requires the reduced graph $G'$ and its isostatic
completion $H$ to be 2-trees as in Section \ref{sec:2-tree-reduction}
or to be a low Cayley complexity tree-decomposable graph as in Section
\ref{sec:tdecomp}. Clearly these problems have deterministic
polynomial time algorithms, the algorithms run in time exponential in
$k$.

We discuss the complexity of the restricted 
OMD problem (when $k$ is part of the input) 
in Section \ref{sec:conclusion}.

\subsection{Optimal Modification, Completion and Recombination: formal
connections}
%
The OMD problem is closely related to a well-studied problem of
completion of an under-constrained system to an isostatic one with a
small DR-plan.
\begin{observation}
\label{obs:OC_to_OMB}
    The (decision version of) the {\bf optimal completion problem
    (OC)} from \cite{bib:survey, j-a, fang} is OMD$_0$.
\end{observation}
In fact, a \dfn{restricted OC} problem was studied by \cite{j-a}
requiring the completion to be tree-decomposable. 
%It is not clear if
%the reverse reduction holds, i.e, is OMD reducible to OC?

@@

This reduction is used also for transferring  algorithms for optimal
DR-planning, recombination, completion, OMD, and other problems 
from bar-joint systems to 
so-called \dfn{multi-body pin} define in Section \ref{sec:bodypin}
by showing that the corresponding problems for the latter are reduced
to the corresponding problems on bar-joint systems.

%\note This section deals only with bar-joint systems, however,
%extensions of several of these problems, approaches and solutions to
%other qusecs beyond  bar-joint - specifically pinned line incidence
%systems and multi-body-pin systems will be expanded in Sections
% \ref{sec:pinnedline} and \ref{sec:bodypin}.

### 2014-12-18 doc/GMP2015/s07_problempinning.tex
Added the open questions to the conclusion

\begin{observation}
    While the proof for Theorem \ref{thm:1dofcase} gives us a DR-plan with minimum fanin, we did not consider the algebraic complexity of realizing the DR-plan. If that is preferred, we can no longer only consider the deepest nodes.
\end{observation}

@@

\begin{openproblem}
    What is the complexity of the optimal completion problem when there are more than 2-dof. For higher number of dofs, the $(k,l)$ characterization is no longer matroidal \cite{Lee:2007:PGA}.
\end{openproblem}

>>>>

\begin{observation}
\label{obs:algebraic_completion}
    While the proof for Theorem \ref{thm:1dofcase} gives us a DR-plan with minimum fanin, we did not consider the algebraic complexity of realizing the DR-plan. If that is preferred, we can no longer only consider the deepest nodes.
\end{observation}

@@

### 2014-12-18 doc/GMP2015/s09_conclusion.tex
Added the open questions to the conclusion

\section{Conclusion}
We have worked to navigate the complexity barriers faced by the general DR-plan and recombination problem. To this end we have defined a new canonical DR-plan and given an effiecient ($O(n^2)$) algorithm to find the DR-plan for specific types of 2D qusecs.

@@

Throughout the paper, we raised some open questions and future areas of research. These include: completion of body-hyper-pin qusecs with more than 2-dof, \todo{Add a general synopsis of other questions}

>>>>

\section{Conclusion}
\bibliography{paper}

We have worked to navigate the complexity barriers faced by the general DR-plan and recombination problem. To this end we have defined a new canonical DR-plan and given an effiecient ($O(n^2)$) algorithm to find the DR-plan for specific types of 2D qusecs.

@@

\subsection{Furture Work}
Throughout the process, we have also raised a few open questions. The first 2 come from Section \ref{sec:recomb}. The first has to do with an actual algorithm for finding an OMD that follows the theory we laid out:

\begin{openproblem}    
What is the complexity of the restricted OMD problem?
This has the potential to be difficult. For example, when the
isostatic completion $H$ is required to be a 2-tree the restricted OMD
problem is reducible to the maximum spanning series-parallel subgraph
problem shown by \cite{cai1993spanning} to be NP-complete even if the input
graph is planar of maximum degree at most 6. However, since the OMD
problem has other input restrictions such as not having any proper
isostatic subgraphs, it is not clear if the reverse reduction exists
and hence it is unclear whether the OMD problem is NP-complete.

The same holds for the restricted OMD problem where the isostatic
completion $H$ is required to be a tree-decomposable graph of low
Cayley complexity (i.e, have special, small DR-plans). One potential
obstacle to an indecomposable graph $G$'s membership in the restricted
OMD$_k$ for small $k$ is if $G$ is tri-connected and has large girth.
In fact, 6-connected (hence rigid) graphs with arbitrarily large girth
have been constructed in \cite{servatius2000rigidity}.
\end{openproblem}

The next is the reverse direction of Observation \ref{obs:OC_to_OMD} in Section \ref{sec:table}.

\begin{openproblem}
    Is the OMD (optimal modification for decomposition) problem  
    reducible to the OC (Optimal completion) problem?
\end{openproblem}

The final one comes about due to our limitations of the proof techniquies in Section \ref{sec:bodypin}.

\begin{openproblem}
    What is the complexity of the optimal completion problem when the given graph has more than 2-dof? Our proof for the 1 and 2-dof cases relied heavily on the matroidal properties of their corresponding tightness. For higher number of dofs, the $(k,l)$ characterization is no longer matroidal \cite{Lee:2007:PGA}. Even so, if higher dofs had the same characteristics, Observation \ref{obs:algebraic_completion} raises some problems of finding a completion with small algebraic complexity. Unless some restrictions can be found and taken advantage of, the $k$-dof optimal completion problem would still be $O(n^{k+1})$.

    The major barrier facing the porblem though is that there is no easy way of obtaining a $k$-dof DR-plan in general. 
\end{openproblem}
